z-score T and F
resids by location


---
title: "Condition anaylsis"
output:
  html_document:
    code_folding: hide
---

Running lm(weight ~ length + ...) for now for speed to get a feel for how slopes of the length/weight relationship vary across species and other variables. Will likely move to RE models next.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy = TRUE, fig.width = 12, fig.height = 10) #, cache = TRUE)
```

```{r load libraries, echo = FALSE, message = FALSE}
library(tidyverse)
library(lme4)
library(broom)
library(kableExtra)
library(modelr)
library(data.table)
library(rlang)
library(tidyfast)
```

If newData, then will load raw files, parse, filter and save as 'dat'
```{r newData}
newData = FALSE
date <- 'June4' #suffix for data subdirectory
```


Only need to run this with new data - data output as 'dat'
```{r fetch data}
if(newData) {

  #bring in all of the fish size data
  fish <- list.files(paste0("D:/projects/ecoDrought/bodySize/All_Size_inputs/Size_inputs_", date), pattern = "*.txt", full.names = T)
  
  txt_files_df <- lapply(fish, function(x) {read.table(file = x, header = T, sep =",")})
  
  all_fish <- do.call("rbind", lapply(txt_files_df, as.data.frame))
  
  ##bring in the covariate data
  covs <- read.csv("D:/projects/ecoDrought/bodySize/All_Size_inputs/covariates_size_analysis.csv")
  
  #merge fish data with covariate data
  all_fish_init<-merge(all_fish, covs, by = "RALLID")
  
  #Select only those fish of interest
  
  #species of interest    
  sinc <- c("Bonneville Cutthroat Trout","Colorado River Cutthroat Trout","Redband Trout","Bull Trout","Brook Trout","Mountain Whitefish","Brown Trout","Westslope Cutthroat Trout", "Yellowstone Cutthroat Trout","Rainbow Trout")
  
  #exclude weir data
  nw <- c("Lake","stream")
  
  dat0 <- all_fish_init %>%
    filter(species %in% sinc, site_type %in% nw,
           !is.na(Weight), Length > 75) %>%
    rename(weight = Weight, length = Length) %>%
    mutate(log10Weight = log10(weight), log10Length = log10(length))
  
  # Species-specific LWE regressions so we can add residuals to dataset
  lwModel <- function(df) {
    lm(log10Weight ~ log10Length, data = df)
  }
  
  datBySpecies <- dat0 %>%
    group_by(species) %>% 
    nest() %>%
    mutate(model = map(data, lwModel))
           
  datBySpecies <- datBySpecies %>% mutate(resids = map2(data, model, add_residuals))

  dat <- dt_unnest(datBySpecies, resids) # unnest() from tidyverse is so slow it never finishes
  
  dat <- dat %>%
    group_by(location) %>%
    mutate(daStd = (log(drain_area_km2) - (mean(log(drain_area_km2)))) / sd(log(drain_area_km2)),
           sFStd = (log(summerF) - (mean(log(summerF + 0.0001), na.rm=TRUE))) / sd(log(summerF + 0.0001), na.rm=TRUE),
           sTStd = (log(summerT) - (mean(log(summerT), na.rm=TRUE))) / sd(log(summerT), na.rm=TRUE),
           slopeStd = (SLOPE - mean(SLOPE)) / sd(SLOPE),
           rdStd = (log(rel_density) - (mean(log(rel_density), na.rm=TRUE))) / sd(log(rel_density), na.rm=TRUE)) %>%
    ungroup()
  
  speciesList <- unique(dat$species)
  
  save(dat, file =paste0("D:/projects/ecoDrought/bodySize/All_Size_inputs/Size_inputs_", date,"/dat.R"))
  
  rm(all_fish_init, all_fish, dat0)
}
```

```{r raw data plots}
if(newData) {
  for(i in c(1,2,4,5,6,7,8,9)) {
    print(i)
    
    ggplot(dat %>% filter(species %in% c(sinc[i])), aes(log10Length, log10Weight, color = Lake)) +
      geom_point(alpha = 0.1) +
      geom_smooth(method = 'lm') +
      facet_wrap(~ species)
    
    ggsave(paste0("D:/projects/ecoDrought/bodySize/All_Size_inputs/ecoDrought_conditionAnalysis/charts/LW_",sinc[i],".png"))
    
    ggplot(dat%>%filter(species == "Brown Trout"), aes(log10Length, log10Weight, color = Location)) +
      #geom_point(alpha = 0.1) +
      geom_smooth(aes(linetype = factor(Lake)), method = 'lm') +
      facet_wrap(~ species)
    
  }
}
  
  
```

```{r load data if no new data}
if(!newData){
  load(paste0("D:/projects/ecoDrought/bodySize/All_Size_inputs/Size_inputs_", date,"/dat.R"))
  speciesList <- unique(dat$species)
}
```


***
# LW relationship analysis section
***

## Species differences
Species have significantly different LW relationships, although LW regression lines overlap considerably.
No random effects yet - lmer takes a long time to run (may try bam, https://m-clark.github.io/posts/2019-10-20-big-mixed-models/)
```{r species effect on LW relationship?}

if(newData) {
    ggplot(dat, aes(log10Length, log10Weight, color = species)) +
    geom_point(alpha = 0.01) +
    geom_smooth(method = 'lm') 
   
    ggsave(paste0("D:/projects/ecoDrought/bodySize/All_Size_inputs/ecoDrought_conditionAnalysis/charts/LWbySpecies.png"))
}

#modSpp1 <- lmer(log10Weight ~ log10Length * species + 1|HUC8_Name, data = dat) very slow
modSpp0 <- lm(log10Weight ~ log10Length, data = dat)
modSpp1 <- lm(log10Weight ~ log10Length * species, data = dat)


AIC(modSpp0, modSpp1)
# species have different slopes and intercepts
kable(anova(modSpp1)) %>% kable_styling(font_size = 12) 
kable(tidy(modSpp1), digits = 3) %>% kable_styling(font_size = 12) %>% kable_styling(font_size = 12)
```

## Lake/stream differences
LW relationships differ between lakes and streams. Intercepts are higher and slopes smaller in streams compared to lakes. Except for Rainbow Trout, which has opposite pattern
```{r lake vs. stream}

modLS1 <- lm(log10Weight ~ log10Length * species * Lake, data = dat)

AIC(modSpp1, modLS1)
kable(anova(modLS1)) %>% kable_styling(font_size = 12) 
kable(tidy(modLS1), digits = 3) %>% kable_styling(font_size = 12) 
```

## Stream order
Mixed affects among species
```{r stream order for streams}

modSO0 <- lm(log10Weight ~ log10Length * species, data = dat %>% filter(Lake == 0))
modSO1 <- lm(log10Weight ~ log10Length * species * Str_Order, data = dat %>% filter(Lake == 0))

AIC(modSO0, modSO1)
kable(anova(modSO1)) %>% kable_styling(font_size = 12) 
#summary(modSO1)

kable(tidy(modSO1), digits = 3) %>% kable_styling(font_size = 12)
```


## Drainage area - stream
Drainage area effect seems to only affect Bull Trout LW relationship. Increase in slope with drainage area for Bull Trout.
```{r drainage area effect streams}

modDA0 <- lm(log10Weight ~ log10Length * species, data = dat %>% filter(Lake == 0))
modDA1 <- lm(log10Weight ~ log10Length * species * drain_area_km2, data = dat %>% filter(Lake == 0))

AIC(modDA0, modDA1)
kable(anova(modDA1)) %>% kable_styling(font_size = 12) 
kable(tidy(modDA1), digits = 3) %>% kable_styling(font_size = 12)
```

## Drainage area - Lake
```{r drainage area effect Lakes}

modDAL0 <- lm(log10Weight ~ log10Length * species, data = dat %>% filter(Lake == 0))
modDAL1 <- lm(log10Weight ~ log10Length * species * drain_area_km2, data = dat %>% filter(Lake == 0))

AIC(modDAL0, modDAL1)
kable(anova(modDAL1)) %>% kable_styling(font_size = 12) 
kable(tidy(modDAL1), digits = 3) %>% kable_styling(font_size = 12)

```

## Distance to lake or stream
Smaller slopes for most species as f(distance to lake)
```{r distance to lake for streams}

modKMLake0 <- lm(log10Weight ~ log10Length * species, data = dat %>% filter(Lake == 0))
modKMLake1 <- lm(log10Weight ~ log10Length * species * KM_Lake, data = dat %>% filter(Lake == 0))

AIC(modKMLake0, modKMLake1)
kable(anova(modKMLake1)) %>% kable_styling(font_size = 12) 
kable(tidy(modKMLake1), digits = 3) %>% kable_styling(font_size = 12)
```

## Distance to 5th order river
Mixed effect on slope among species. Neg effect on slope for Bull Trout
```{r distance to 5th order river for streams}

modKM50 <- lm(log10Weight ~ log10Length * species, data = dat %>% filter(Lake == 0))
modKM51 <- lm(log10Weight ~ log10Length * species * KM_5th, data = dat %>% filter(Lake == 0))

AIC(modKM50, modKM51)
kable(anova(modKM51)) %>% kable_styling(font_size = 12) 
kable(tidy(modKM51), digits = 3) %>% kable_styling(font_size = 12)
```

## Spring flow effects
Spring Flow increases slope for all species except CR cuts
```{r spring flow effects for streams}

modSF0 <- lm(log10Weight ~ log10Length * species, data = dat %>% filter(Lake == 0))
modSF1 <- lm(log10Weight ~ log10Length * species * springF, data = dat %>% filter(Lake == 0))

AIC(modSF0, modSF1)
kable(anova(modSF1)) %>% kable_styling(font_size = 12) 
kable(tidy(modSF1), digits = 3) %>% kable_styling(font_size = 12)
```


## Spring temp effects
Spring temp increases slope for most species
```{r spring temp effects for streams}

modST0 <- lm(log10Weight ~ log10Length * species, data = dat %>% filter(Lake == 0))
modST1 <- lm(log10Weight ~ log10Length * species * springT, data = dat %>% filter(Lake == 0))

AIC(modST0, modST1)
kable(anova(modST1)) %>% kable_styling(font_size = 12) 
kable(tidy(modST1), digits = 3) %>% kable_styling(font_size = 12)
```

## Summer flow effects
Summer Flow increases slope for all species except CR cuts
```{r summer flow effects for streams}

modSuF0 <- lm(log10Weight ~ log10Length * species, data = dat %>% filter(Lake == 0))
modSuF1 <- lm(log10Weight ~ log10Length * species * summerF, data = dat %>% filter(Lake == 0))

AIC(modSuF0, modSuF1)
kable(anova(modSuF1)) %>% kable_styling(font_size = 12) 
kable(tidy(modSuF1), digits = 3) %>% kable_styling(font_size = 12)
```


## Summer temp effects
Summer temp increases slope for most species
```{r summer temp effects for streams}

modSuT0 <- lm(log10Weight ~ log10Length * species, data = dat %>% filter(Lake == 0))
modSuT1 <- lm(log10Weight ~ log10Length * species * summerT, data = dat %>% filter(Lake == 0))

AIC(modSuT0, modSuT1)
kable(anova(modSuT1)) %>% kable_styling(font_size = 12) 
kable(tidy(modSuT1), digits = 3) %>% kable_styling(font_size = 12)
```

## Autumn flow effects
Autumn Flow increases LW slope for all species except CR cuts 
```{r autumn flow effects for streams}

modAF0 <- lm(log10Weight ~ log10Length * species, data = dat %>% filter(Lake == 0))
modAF1 <- lm(log10Weight ~ log10Length * species * autumnF, data = dat %>% filter(Lake == 0))

AIC(modAF0, modAF1)
kable(anova(modAF1)) %>% kable_styling(font_size = 12) 
kable(tidy(modAF1), digits = 3) %>% kable_styling(font_size = 12)
```

## Autumn temp effects
Autumn temp *not* significant
```{r autumn temp effects for streams}

modAT0 <- lm(log10Weight ~ log10Length * species, data = dat %>% filter(Lake == 0))
modAT1 <- lm(log10Weight ~ log10Length * species * autumnT, data = dat %>% filter(Lake == 0))

AIC(modAT0, modAT1)
kable(anova(modAT1)) %>% kable_styling(font_size = 12) 
kable(tidy(modAT1), digits = 3) %>% kable_styling(font_size = 12)
```

## Spring temp * flow effects
Strong negative flow * temp interaction for all species
```{r spring temp*flow effects for streams}

modSpTF0 <- lm(log10Weight ~ log10Length * species, data = dat %>% filter(Lake == 0))
modSpTF1 <- lm(log10Weight ~ log10Length * species * springT * springF, data = dat %>% filter(Lake == 0))

AIC(modSpTF0, modSpTF1)
kable(anova(modSpTF1)) %>% kable_styling(font_size = 12) 
kable(tidy(modSpTF1), digits = 3) %>% kable_styling(font_size = 12)
```


## Summer temp*flow effects
Strong negative flow*temp interaction for all species
```{r summer temp*flow effects for streams}

modSuTF0 <- lm(log10Weight ~ log10Length * species, data = dat %>% filter(Lake == 0))
modSuTF1 <- lm(log10Weight ~ log10Length * species * summerT * summerF, data = dat %>% filter(Lake == 0))

AIC(modSuTF0, modSuTF1)
kable(anova(modSuTF1)) %>% kable_styling(font_size = 12) 
kable(tidy(modSuTF1), digits = 3) %>% kable_styling(font_size = 12)
```

***
# Residual analysis section
Analyses of residuals from species-specific LW regressions
***
```{r}

ggplot(dat %>% filter(species == speciesList[1]), aes(x = resid, y = ..ncount.., color = HUC12_NAME)) +
  geom_freqpoly(nbin = 50, show.legend = FALSE) +
  geom_vline(xintercept = 0) +
  facet_wrap(~HUC8_Name)

#  facet_wrap(~HUC12_NAME)

ggplot(dat, aes(factor(Lake), resid)) +
  geom_boxplot(outlier.shape = NA) +
  ylim(c(-0.25, 0.25)) +
  facet_wrap(~species)

ggplot(dat, aes(factor(Str_Order), resid)) +
  geom_boxplot(outlier.shape = NA) +
  ylim(c(-0.25, 0.25)) +
  facet_wrap(~species) 

glance(lm(resid ~ drain_area_km2 * species, data = dat %>% filter(Lake == 0)))
ggplot(dat %>% filter(Lake == 0), aes(drain_area_km2, resid)) +
  #geom_point(alpha = 0.01) +
  geom_smooth(method = 'lm') +
  facet_wrap(~species)

glance(lm(resid ~ KM_Lake * species, data = dat %>% filter(Lake == 0)))
ggplot(dat %>% filter(Lake == 0), aes(KM_Lake, resid)) +
  #geom_point(alpha = 0.01) +
  geom_smooth(method = 'lm') +
  facet_wrap(~species)

glance(lm(resid ~ KM_5th * species, data = dat %>% filter(Lake == 0)))
ggplot(dat %>% filter(Lake == 0), aes(KM_5th, resid)) +
  #geom_point(alpha = 0.01) +
  geom_smooth(method = 'lm') +
  facet_wrap(~species)

glance(lm(resid ~ springF * species, data = dat %>% filter(Lake == 0)))
ggplot(dat %>% filter(Lake == 0), aes(springF, resid)) +
  #geom_point(alpha = 0.01) +
  geom_smooth(method = 'lm') +
  facet_wrap(~species)

glance(lm(resid ~ springT * species, data = dat %>% filter(Lake == 0)))
ggplot(dat %>% filter(Lake == 0), aes(springT, resid)) +
  #geom_point(alpha = 0.01) +
  geom_smooth(method = 'lm') +
  facet_wrap(~species)

glance(lm(resid ~ summerF * species, data = dat %>% filter(Lake == 0)))
ggplot(dat %>% filter(Lake == 0), aes(summerF, resid)) +
  #geom_point(alpha = 0.01) +
  geom_smooth(method = 'lm') +
  facet_wrap(~species)

glance(lm(resid ~ summerT * species, data = dat %>% filter(Lake == 0)))
ggplot(dat %>% filter(Lake == 0), aes(summerT, resid)) +
  #geom_point(alpha = 0.01) +
  geom_smooth(method = 'lm') +
  facet_wrap(~species)

glance(lm(resid ~ autumnF * species, data = dat %>% filter(Lake == 0)))
ggplot(dat %>% filter(Lake == 0), aes(autumnF, resid)) +
  #geom_point(alpha = 0.01) +
  geom_smooth(method = 'lm') +
  facet_wrap(~species)

glance(lm(resid ~ autumnT * species, data = dat %>% filter(Lake == 0)))
ggplot(dat %>% filter(Lake == 0), aes(autumnT, resid)) +
  #geom_point(alpha = 0.01) +
  geom_smooth(method = 'lm') +
  facet_wrap(~species)

glance(lm(resid ~ rel_density * species, data = dat %>% filter(Lake == 0, rel_density < 2000)))
ggplot(dat %>% filter(Lake == 0), aes(rel_density, resid)) +
  #geom_point(alpha = 0.01) +
  geom_smooth(method = 'lm') +
  facet_wrap(~species)

```

***
Spatially-nested lmer() by species to explore spatial structuring of variation in LW regression residuals
HUC12 nested within HUC8 nested within Location

```{r spatially-nested lmer by species}

# build up hierarchical random effects for each species 
## Hierarchical graphs for huc12/huc8/location 
  lmerModel <- function(df) {
    lmer(resid ~ 1 + (1|location/HUC8_Name/HUC12_NAME), data = df)
  }

  reBySpecies <- function(mod, species){
    re <- as.data.frame(ranef(mod))

    re12 <- re %>%
      filter(grpvar == 'HUC12_NAME:(HUC8_Name:location)') %>%
      mutate(huc12 = str_split(grp, ":", simplify = TRUE)[,1],
             huc8 = str_split(grp, ":", simplify = TRUE)[,2],
             loc = str_split(grp, ":", simplify = TRUE)[,3]) %>%
      rename(condval12 = condval)
  
    re8 <- re %>%
      filter(grpvar == 'HUC8_Name:location') %>%
      mutate(loc = str_split(grp, ":", simplify = TRUE)[,2],
             huc8 = str_split(grp, ":", simplify = TRUE)[,1]) %>%
      rename(condval8 = condval)
    
    reLoc <- re %>%
      filter(grpvar == 'location') %>%
      mutate(loc = grp) %>%
      rename(condvalLoc = condval)%>% 
      select(condvalLoc, loc)
    
    reAll1 <- left_join(re8, reLoc) %>% select(condval8, loc, huc8, condvalLoc)
    reAll <- left_join(re12, reAll1) %>% arrange(loc, huc8, huc12)
    reAll <- reAll %>%
      mutate(condvalLoc8 = condvalLoc + condval8,
             condvalLoc812 = condvalLoc + condval8 + condval12)
    
    gg <- ggplot(reAll, aes(condvalLoc812, huc12)) +
      geom_point(color = '#ff9a36') +
      geom_point(aes(condvalLoc8, huc12), color = '#3f7bc4') +
      geom_point(aes(condvalLoc, huc12, shape = factor(loc)), color = '#bdb2a8') +
      geom_vline(xintercept = 0) +
      scale_y_discrete(guide = guide_none(title = NULL)) +
      scale_x_continuous("Residual from species-specific LW relationship") +
      ggtitle(species) +
      facet_wrap(~huc8)
    
    ggsave(paste0("D:/projects/ecoDrought/bodySize/All_Size_inputs/ecoDrought_conditionAnalysis/charts/hierResids_",species,".png"))
    
    return(gg)
  }
  
##  
    # Charts of nested random effects 
  datBySpeciesRE <- dat %>%
    filter(species %in% speciesList[c(1,3,4,5,7)]) %>%
    #filter(species %in% speciesList[5]) %>% #
    group_by(species) %>% 
    nest() %>%
    mutate(model = map(data, lmerModel)) %>%
    mutate(charts = map2(model, species, reBySpecies))

  datBySpeciesRE$charts
  
  ## SDs of nested levels ################
  datBySpeciesRESD <- datBySpeciesRE %>%
    mutate(tidy = map(model, broom::tidy)) %>% 
    unnest(tidy) %>%
    select(species, estimate, term, group) %>%
    filter(!term == '(Intercept)')
  
  ggSD <- ggplot(datBySpeciesRESD, aes(species,estimate, fill = group)) +
    geom_col(position = "dodge") +
    scale_y_continuous("Standard deviation of nested LW residuals")
  ggSD
  

##############################################################################  
  # some species have data for one location only #2 6 8 9
  # Colorado River Cutthroat Trout model has singularity - ignoring for now
  ## Hierarchical graphs for huc12/huc8 
  lmerModelNoLocation <- function(df) {
    lmer(resid ~ 1 + (1|HUC8_Name/HUC12_NAME), data = df)
  }
  
  # build up hierarchical random effects for each species 
  reBySpecies812 <- function(mod, species){
    re <- as.data.frame(ranef(mod))

    re12 <- re %>%
      filter(grpvar == 'HUC12_NAME:HUC8_Name') %>%
      mutate(huc12 = str_split(grp, ":", simplify = TRUE)[,1],
             huc8 = str_split(grp, ":", simplify = TRUE)[,2]
             ) %>%
      rename(condval12 = condval)

    re8 <- re %>%
      filter(grpvar == 'HUC8_Name') %>%
      mutate(huc8 = grp) %>%
      rename(condval8 = condval) %>% 
      select(condval8, huc8)
    
    reAll <- left_join(re12, re8) %>% arrange(huc8, huc12)
    reAll <- reAll %>%
      mutate(condval8 = condval8,
             condval812 = condval8 + condval12)
    
    gg <- ggplot(reAll, aes(condval812, huc12)) +
      geom_point(color = '#ff9a36') +
      geom_point(aes(condval8, huc12), color = '#3f7bc4') +
      geom_vline(xintercept = 0) +
      scale_y_discrete(guide = guide_none(title = NULL)) +
      scale_x_continuous("Residual from species-specific LW relationship") +
      ggtitle(species) +
      facet_wrap(~huc8)
    
    ggsave(paste0("D:/projects/ecoDrought/bodySize/All_Size_inputs/ecoDrought_conditionAnalysis/charts/hierResids_",species,".png"))
    
    return(gg)
  }
  
  # Charts of nested random effects 
  datBySpeciesRENoLocation <- dat %>%
    filter(species %in% speciesList[c(2,8,9)]) %>%
    group_by(species) %>% 
    nest() %>%
    mutate(model = map(data, lmerModelNoLocation)) %>%
    mutate(charts = map2(model, species, reBySpecies812))
  
  datBySpeciesRENoLocation$charts 
  
  ## SDs of nested levels ################
  datBySpeciesRENoLocationSD <- datBySpeciesRENoLocation %>%
    mutate(tidy = map(model, broom::tidy)) %>% 
    unnest(tidy) %>%
    select(species, estimate, term, group) %>%
    filter(!term == '(Intercept)')
  
  ggNoLocationSD <- ggplot(datBySpeciesRENoLocationSD, aes(species,estimate, fill = group)) +
    geom_col(position = "dodge") +
    scale_y_continuous("Standard deviation of nested LW residuals") 
  ggNoLocationSD 
  
```


***
# Residual means by waterbody
Analyze means of residuals by waterbody. Speeds up lmer() and reduces df inflation from individual observations.
Remove waterbodies with < 10 observations.
Look in depth at lm() for Brook Trout

```{r means by waterbody}

datByWB <- dat %>%
  group_by(species, Lake, WATERBODY, location, HUC8_Name, HUC12_NAME, rdStd, rel_density,
           sFStd, sTStd, daStd, Str_Order, KM_4th, KM_Lake) %>%
  summarize(meanResid = mean(resid, na.rm = TRUE),
            sdResid = sd(resid, na.rm = TRUE),
            n = n(),
            meanLength = mean(log10Length, na.rm = TRUE),
            meanWeight = mean(log10Weight, na.rm = TRUE)) %>%
  filter(n > 10) %>%
  ungroup()

## bkt deep dive
datBKT <- datByWB %>% filter(species == "Brook Trout")

b0 <- lmer(meanResid ~ 1 + (1|location/HUC8_Name), data = datBKT %>% filter(Lake == 0))
b1 <- lmer(meanResid ~ 1 + rdStd + (1|location/HUC8_Name), data = datBKT %>% filter(Lake == 0))

AIC(b0, b1)
tidy(b1)

ggplot(datBKT %>% filter(Lake == 0), aes(rdStd, meanResid)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = 'lm') +
  facet_wrap(~location)

# summerF, summerT, drain_area_km2, Str_Order, KM_4th,KM_Lake
ggplot(datBKT %>% filter(Lake == 0, location == 'MT'), aes(rdStd, meanResid)) +
  geom_point(aes(color = daStd)) +
  geom_smooth(method = 'lm') +
  scale_color_viridis_c() +
  facet_wrap(~location)

b2 <- lmer(meanResid ~ 1 + daStd + (1|location/HUC8_Name), data = datBKT %>% filter(Lake == 0))
b3 <- lmer(meanResid ~ 1 + daStd * rdStd + (1|location/HUC8_Name), data = datBKT %>% filter(Lake == 0))

AIC(b0, b1, b2, b3)
glance(b3)

b4 <- lmer(meanResid ~ 1 + daStd * meanLength + (1|location/HUC8_Name), data = datBKT %>% filter(Lake == 0))
AIC(b0, b1, b2, b3, b4) %>% arrange(AIC)

# are the random effects sucking up all the variance? Try just lm() to see how var can get explained
blm0 <- lm(meanResid ~ 1, data = datBKT %>% filter(Lake == 0))
blm1 <- lm(meanResid ~ 1 + location, data = datBKT %>% filter(Lake == 0))
blm2 <- lm(meanResid ~ 1 + rdStd * location, data = datBKT %>% filter(Lake == 0))
blm3 <- lm(meanResid ~ 1 + daStd * location, data = datBKT %>% filter(Lake == 0))
blm4 <- lm(meanResid ~ 1 + sFStd * location, data = datBKT %>% filter(Lake == 0))
blm5 <- lm(meanResid ~ 1 + sTStd * location, data = datBKT %>% filter(Lake == 0))
blm6 <- lm(meanResid ~ 1 + meanLength * location, data = datBKT %>% filter(Lake == 0))
blm7 <- lm(meanResid ~ 1 + Str_Order * location, data = datBKT %>% filter(Lake == 0))
blm8 <- lm(meanResid ~ 1 + KM_4th * location, data = datBKT %>% filter(Lake == 0))
blm9 <- lm(meanResid ~ 1 + rdStd * daStd * location, data = datBKT %>% filter(Lake == 0))
blm10 <- lm(meanResid ~ 1 + sFStd * sTStd * location, data = datBKT %>% filter(Lake == 0))
blm11 <- lm(meanResid ~ 1 + meanLength * sFStd * location, data = datBKT %>% filter(Lake == 0))
blm12 <- lm(meanResid ~ 1 + meanLength * sTStd * location, data = datBKT %>% filter(Lake == 0))
blm13 <- lm(meanResid ~ 1 + meanLength * sFStd * sTStd * location, data = datBKT %>% filter(Lake == 0))
blmMega <- lm(meanResid ~ 1 + meanLength * sFStd * sTStd * Str_Order * KM_4th * location * sFStd * sTStd, data = datBKT %>% filter(Lake == 0))

AIC(blm0,blm1,blm2,blm3,blm4,blm5,blm6,blm7,blm8,blm9,blm10,blm11,blm12,blm13,blmMega) %>% arrange(AIC)
glance(blm10)
glance(blm13)
glance(blmMega)

ggplot(datBKT %>% filter(Lake == 0), aes(sFStd, meanResid)) +
  geom_point(aes(color = sTStd)) +
  geom_smooth(method = 'lm') +
  scale_color_viridis_c() +
  facet_wrap(~location)

ggplot(datBKT %>% filter(Lake == 0, location == 'MT'), aes(sFStd, sTStd, z = meanResid)) +
  geom_density2d() 


```

