---
title: "Condition anaylsis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load libraries, echo = FALSE}
library(tidyverse)
library(lme4)
```

If newData, then will load raw files, parse, filter and save as 'dat'
```{r newData?}
newData = FALSE
date <- 'May27' #suffix for data subdriectory
```


Only need to run this with new data - data output as 'dat'
```{r fetch data}

if(newData){

  #bring in all of the fish size data
  fish <- list.files(paste0("D:/projects/ecoDrought/bodySize/All_Size_inputs/Size_inputs_", date), pattern = "*.txt", full.names = T)
  
  txt_files_df <- lapply(fish, function(x) {read.table(file = x, header = T, sep =",")})
  
  all_fish <- do.call("rbind", lapply(txt_files_df, as.data.frame))
  
  ##bring in the covariate data
  covs <- read.csv("D:/projects/ecoDrought/bodySize/All_Size_inputs/covariates_size_analysis.csv")
  
  #merge fish data with covariate data
  all_fish_init<-merge(all_fish, covs, by = "RALLID")
  
  #Select only those fish of interest
  
  #species of interest AND    #get rid of weir data
  sinc <- c("Bonneville Cutthroat Trout","Colorado River Cutthroat Trout","Redband Trout","Bull Trout","Brook Trout","Mountain Whitefish","Brown Trout","Westslope Cutthroat Trout", "Yellowstone Cutthroat Trout","Rainbow Trout")
  
  nw <- c("Lake","stream")
  
  dat <- all_fish_init %>%
    filter(species %in% sinc, site_type %in% nw,
           !is.na(Weight), Length > 75) %>%
    rename(weight = Weight, length = Length) %>%
    mutate(log10Weight = log10(weight), log10Length = log10(length))
    
  save(dat, file =paste0("D:/projects/ecoDrought/bodySize/All_Size_inputs/Size_inputs_", date,"/dat.R"))
  
  rm(all_fish_init, all_fish)
}
```

```{r raw data plots}

if(newData) {
  for(i in c(1,2,4,5,6,7,8,9)) {
    print(i)
    
    ggplot(dat %>% filter(species %in% c(sinc[i])), aes(log10Length, log10Weight, color = site_type)) +
      geom_point(alpha = 0.1) +
      geom_smooth(method = 'lm') +
      facet_wrap(~ species)
    
    ggsave(paste0("D:/projects/ecoDrought/bodySize/All_Size_inputs/ecoDrought_conditionAnalysis/charts/LW_",sinc[i],".png"))
  }
}
  
  
```

```{r load data}
if(!newData){
  load(paste0("D:/projects/ecoDrought/bodySize/All_Size_inputs/Size_inputs_", date,"/dat.R"))
  speciesList <- unique(dat$species)
}
```

Species have different LW relationships.
No random effects yet - lmer takes a long time to run (may try bam, https://m-clark.github.io/posts/2019-10-20-big-mixed-models/)
```{r species effect on LW relationship?}
if(newData) {
    ggplot(dat, aes(log10Length, log10Weight, color = species)) +
    geom_point(alpha = 0.1) +
    geom_smooth(method = 'lm') 
   
    ggsave(paste0("D:/projects/ecoDrought/bodySize/All_Size_inputs/ecoDrought_conditionAnalysis/charts/LWbySpecies.png"))
}

#modSpp1 <- lmer(log10Weight ~ log10Length * species + 1|HUC8_Name, data = dat) very slow
modSpp0 <- lm(log10Weight ~ log10Length, data = dat)
modSpp1 <- lm(log10Weight ~ log10Length * species, data = dat)


AIC(modSpp0, modSpp1)
# species have different slopes and intercepts
anova(modSpp1)
summary(modSpp1)
```

LW relationships differ between lakes and streams. Intercepts are higher and slopes smaller in streams compared to lakes. Except for Rainbow Trout, which has opposite pattern
```{r lake vs. stream}

modLS1 <- lm(log10Weight ~ log10Length * species * site_type, data = dat)

AIC(modSpp1, modLS1)
anova(modLS1)
summary(modLS1)
```

Stream order or drainage area effect?
```{r stream order effect}

modDA0 <- lm(log10Weight ~ log10Length * species, data = dat %>% filter(site_type == "stream"))
modDA1 <- lm(log10Weight ~ log10Length * species * drain_area_km2, data = dat %>% filter(site_type == "stream"))

AIC(modDA0, modDA1)
anova(modDA1)
summary(modDA1)
```

Lake size effect?
Temp and flow effects?


